Near Optimal Behavior with Approximate Abstraction

### 2016-02-04 paper/results_discussion.tex
Shortened nChain a bit

\section{Approximate Abstraction on Example Domains}
%Explanation of what abstraction is used
We run experiments on aggregation functions in the $\epQ$ family of approximate abstractions. For each trial our aggregation greedily groups ground states into abstract states that satisfy the $\epQ$ criteria. The order in which ground states are added is randomized, so there is randomization across trials. Every ground state is equally weighted in its abstract state.

%Explanation of what plots done
For each domain we report two quantities as a function of epsilon with \%95 confidence bars. First, we compare the number of states in the abstract \ac{MDP} to different values of $\epsilon$, shown in Figure~\ref{fig:main_empirical_results1}. The smaller this value, the smaller the state space of the $\ac{MDP}$ that the agent must plan over. Second, we report the value under the abstract policy of the initial ground state, shown in Figure~\ref{fig:main_empirical_results2}. In the Taxi and Random domains, 200 trials are run for each data point, whereas 20 trials are run for data points in Minefield and NChain.

>>>>

\section{Approximate Abstraction on Example Domains}
%Explanation of what abstraction is used
We run experiments on aggregation functions in the $\epQ$ family of approximate abstractions. For each trial our aggregation greedily groups ground states into abstract states that in a way that satisfies the $\epQ$ criteria. The order in which ground states are grouped is randomized, so there is randomization across trials. Every ground state is equally weighted in its abstract state.

%Explanation of what plots done
For each domain we report two quantities as a function of epsilon with 95\% confidence bars. First, we compare the number of states in the abstract \ac{MDP} for different values of $\epsilon$, shown in Figure~\ref{fig:main_empirical_results1}. The smaller the number of abstract states, the smaller the state space of the $\ac{MDP}$ that the agent must plan over. Second, we report the value under the abstract policy of the initial ground state, shown in Figure~\ref{fig:main_empirical_results2}. In the Taxi and Random domains, 200 trials are run for each data point, whereas 20 trials are run for data points in Minefield and NChain.
